A Discontinuous Petrov-Galerkin method for convection-diffusion problems

### 2013-07-30 docs/Jesse/Dissertation/confusionDPGIntro.tex

The majority of this chapter will focus on the convection-diffusion problem using the abstract theory that we have discussed in the previous chapter. In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve this model problem and analyze its behavior as $\epsilon\rightarrow 0$. Our goal is to show the robustness of the method with respect to $\epsilon$, and demonstrate its usefulness as a numerical method for solving singular-perturbed problems.

@@

\seclab{sec:modelSec}

The convection-diffusion problem is given on a domain
$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
\begin{equation}
\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
\end{equation}
which can be cast into the first order form on the group variable
$\LRp{u,\sigma}$ as
\begin{equation}
\eqnlab{CDstrong}
A \LRp{u,\sigma} \coloneqq \LRs {
\begin{array}{c}
\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
\end{array}} = \LRs{
\begin{array}{c}
f \\ 0
\end{array}
}.
\end{equation}
Using the abstract ultra-weak formulation developed in Section
\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
obtain
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
  \jump{v} }_{\Gh},
\end{align*}
where $\LRp{v, \tau}$ is the group test function. It should be pointed
out that the divergence and gradient operators are understood to act
element-wise on test functions $\LRp{v, \tau}$ in the broken graph
space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
canonical test norm can be written as
\[
\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
    div},K)}^2,
\]
where
\[
\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2.
\]

In order to define the proper norm on the trial space, boundary
conditions need to be specified. We begin by splitting the boundary
$\Gamma$ as follows
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\}, \quad {\rm
  (inflow)}\\ \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\},
\quad {\rm (outflow)}\\ \Gamma_{0} &\coloneqq \{x\in \Gamma;
\beta_n(x) = 0\},
\end{align*}
where $\beta_n \coloneqq \beta \cdot n$.
Previous work in \cite{DPGrobustness} adopted Dirichlet boundary
conditions everywhere on $\Gamma$.  
%and we could obtain the robustness only with special weighted norms in which the weight varied spatially. 
We employ instead the inflow
condition of Hesthaven \etal \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n  = u_0, \quad \text{on } \Gm,
\]
instead of $\beta_n u = u_0$. The former resembles the latter
as $\epsilon$ approaches zero\footnote{For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$ will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.}; however, the latter induces a more ``well-behaved" adjoint problem than the former, which, as we will discuss, affects the performance of DPG.

On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
\[
u = 0, \quad \text{on } \Gp.
\]
The material in this chapter is intended to act as an extension of the theory developed by Heuer and Demkowicz in \cite{DPGrobustness}. The primary focus of this chapter is to analyze the DPG method and extend previous results under this new choice of inflow boundary conditions. The difference in the performance of DPG under both new and old boundary conditions is connected to the difference in the adjoint problems induced under each boundary condition. The secondary contribution of this work will be to analyze the performance of DPG under a new mesh-dependent test norm.

\subsection{Norms on $U$}

With the above boundary conditions at hand, the ultra-weak formulation
\eqnref{uweak} can be fitted in the abstract form \eqnref{variationEq}
as
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right), \left( v,
\tau\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad
v\right)_{\Oh} \\
&- \LRa{ \jump{\tau\cdot n}, \widehat{u} }_{\Gh
  \setminus \Gp} + \LRa{ \widehat{f}_n, \jump{v} }_{\Gamma_h \setminus
  \Gm} =  \left(f, v\right) -
\LRa{ u_0, v }_{\Gamma_-} = l\left(\left(v, \tau\right)\right),
\end{align*}
which, after using the setting in Section \secref{abstractUweak},
suggests the following trial space (see \cite{analysisDPG, Bui-ThanhDemkowiczGhattas11b} for details):
\begin{align*}
u, \sigma \in \L, \quad \text{and } \LRp{\uh,\fnh} \in
\gamma\LRp{D\LRp{A}} \subset \gamma\LRp{  H^1(\Omega) \times
H({\rm div}, \Omega)} = H^{\frac{1}{2}}\left(\Gh\right) \times H^{-\frac{1}{2}}\left(\Gh\right).
\end{align*}
The space for $u$ and $\sigma$ are simply scalar and vector $L^2$ spaces over $\Omega$, while the space for $\left(\uh,\fnh\right)$ is the trace space of the graph space of the operator $A$ subject to the boundary conditions.

The minimum energy extension norm \eqnref{MEnorm} now reads
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gh\setminus
    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}, \\ \|\widehat{f}_n\|
&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
  0, \left. q\cdot n \right |_{\Gh\setminus
    \Gamma_-} = \widehat{f}_n}
\|q\|_{H({\rm div},\Omega)}.
\end{align*}
As a result, the canonical norm on $U$ is given by
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U^2 = 
\|u\|_{L^2(\Oh)}^2 + \|\sigma\|_{L^2(\Oh)}^2 +
\|\widehat{u}\|^2 + \|\widehat{f}_n\|^2.
\]

\subsection{Norms on $V$}

%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Oh$. 
As $\tau \in H({\rm div},\Oh)$ and $v \in H^1(\Oh)$, we will
construct norms on $v$ and $\tau$ 
which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
norm over a single element
\[
\|\left(v,\tau\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2.
\]
The squared norm over the entire triangulation $\Oh$ is defined to be the squared sum of contributions from each element
\[
\|\left(v,\tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
= \sum_{K\in \Oh} \|\left(v,\tau\right)\|_{H^1(K) \times H({\rm
    div},K)}^2.
\]
The exact norms that we will specify on $V$ will be determined later.

The norms on the skeleton $\Gh$ for $v$ and $\tau$ are defined by duality from the bilinear form
\begin{align*}
\left\|\jump{\tau\cdot n}\right\| &= \left\|\jump{\tau\cdot n}\right\|_{\Gh \setminus \Gamma_+} \coloneqq \sup_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau \cdot n}, w\rangle}{\|w\|_{H^1(\Omega)}},\\
\left\|\jump{v}\right\|&=\left\|\jump{v}\right\|_{\Gh^0 \cup \Gamma_+} \coloneqq \sup_{\eta\in H({\rm div},\Omega), \left.\eta\cdot n\right|_{\Gamma_- \cup \Gamma_0} = 0} \frac{\langle \jump{v}, \eta\cdot n\rangle}{\|\eta\|_{H({\rm div},\Omega)}}.
\end{align*}

\subsection{Approximability of the quasi-optimal test norm}
%\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}
An obvious choice for the test norm would be the quasi-optimal norm; it is the canonical test norm, and DPG has been shown to be well-posed and robust under such an optimal test norm for a large class of problems \cite{DPGrobustness,Bui-ThanhDemkowiczGhattas11b, stokesDPG}. However, computations with the quasi-optimal test norm for convection-diffusion problems turn out to be quite problematic for small diffusion and coarse meshes.

For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(v,\tau\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
\|v\|_{L^2}^2 + \|\tau\|_{L^2}^2.
\]
%We note that the optimal test norm will automatically guarantee the
%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
Use of this norm for the convection-diffusion problem is difficult --- since the problem \eqnref{optvVar} for optimal test functions is local, we can transform the problem over a single element $K$ to the reference element $\widehat{K}$ and show that it is equivalent to a reaction-diffusion system, with diffusion parameter $\frac{\epsilon}{|K|}$, where $|K|$ is the element measure \cite{DBLP:journals/procedia/NiemiCC11}. We refer to the inverse of this parameter $\frac{|K|}{\epsilon}$ as the element Peclet number $\rm Pe$. For a coarse mesh and small diffusion parameter $\epsilon$, we will have a large element Peclet number, and optimal test functions under the quasi-optimal test norm will develop strong boundary layers of width $\rm Pe$, as seen in Figure~\ref{fig:optTestBoundary}.

In the application of DPG in \cite{DPG1,DPG2,DPG3,DPG4}, the approximation of optimal test functions is done using polynomial enrichment. We search for the solution to \eqnref{optvVar} in the enriched test space $\tilde{V} \approx \prod_{K} P^{p+\Delta p}(K)$, where $p$ is the polynomial order of the trial space on a given element $K$.\footnote{$V$ is only \emph{approximately} equal to the space $\prod_{K} P^{p+\Delta p}(K)$. In practice, $V$ is constructed using locally $H^1$-conforming and Raviart-Thomas elements of appropriate order.}  In other words, optimal test functions are approximated element-by-element using polynomials whose order is $\Delta p$ more than the local order of approximation.  Under this scheme, the error in approximation of test functions is tied to the effectiveness of the $p$-method.  Unfortunately, for problems with boundary layers --- including the approximation of test functions under the quasi-optimal test norm --- the $p$-method performs very poorly. As a result of this poor approximation, the numerical solutions of the convection-dominated diffusion equation under DPG using the quasi-optimal test norm tend to be of poor quality, and do not exhibit all the proven properties of DPG (for example, the energy error may increase after mesh refinement, even though, by virtue of DPG delivering a best approximation, the energy error for a coarse mesh must be greater than or equal to the energy error for a finer mesh).  We conclude that the error in approximation of optimal test functions using simple polynomial enrichment pollutes and ruins the performance of DPG under the quasi-optimal test norm.

\begin{figure}[!h]
\centering
\includegraphics[scale=.25]{figs/opt.png}
\caption{$v$ and $\tau$ components of the 1D optimal test functions corresponding to the flux $\widehat{f}_n$ on the right-hand side of a unit element for $\epsilon = 0.01$. The solution has been obtained using automatic $hp$-adaptivity driven by the test norm with the error tolerance set at 1\%.}
\label{fig:optTestBoundary}
\end{figure}

The difficulty in using the quasi-optimal test norm for convection-diffusion is perplexing at first, considering that the quasi-optimal norm has yielded excellent results for the Helmholtz equation and other wave propagation problems.  The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$ --- the singular perturbation parameter. Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are approximated much more accurately using only polynomials over the reference element. Typically, the wavenumbers $k$ of physical interest are $O(100)$ with respect to a unit domain. The corresponding finite element problems will typically be solved on meshes containing approximately $O\!\left(k^d\right)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation. However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$. Solving on under-resolved meshes is thus unavoidable, and the approximability of optimal test functions must be addressed in order to take advantage of the properties of DPG.

Resolving such boundary layers present in test functions under the quasi-optimal test norm has been investigated numerically using specially designed (Shishkin) subgrid meshes by Niemi, Collier, and Calo in
\cite{DBLP:journals/procedia/NiemiCC11}.  However, even with Shishkin meshes, the approximation of optimal test functions under the quasi-optimal norm is far more expensive and complex to implement than approximation of test functions using a simple $p$-enriched space for $V$. We therefore aim instead to design a test norm that does not induce boundary layers, but still delivers good approximation results over a range of $\epsilon$.

\subsection{Analysis of a DPG test norm}
\seclab{sec:testNormSec}
We are interested in computing DPG optimal test functions for the convection-diffusion equation with very small values of $\epsilon$; due to the difficulty of approximating optimal test functions, we conclude that the use of the quasi-optimal test norm is infeasible towards this goal.

However, if we naively choose a test norm that does not generate boundary layers, the performance of DPG may be adversely affected. For example, if $\|\left(v,\tau\right)\|_V^2 = \|v\|_{H^1(\Omega_h)}^2 + \|\tau\|^2_{H({\rm div},\Omega_h)}$, the $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm, then the corresponding test functions will be smooth and free of boundary layers; however, the performance of DPG will provide approximations which worsen in quality as $\epsilon$ becomes very small \cite{DPG3,DPGrobustness}.

Our goal is to construct a test norm that compromises between performance of DPG and approximability of test functions.  This test norm should not produce boundary layers in the optimal test functions, but still induce an energy norm that yields good approximation properties for small $\epsilon$. We note that, even under the quasi-optimal norm, the norms on the flux and trace variables will likely depend on $\epsilon$. Thus, we aim to construct a test norm for which the DPG method will be robust in $\epsilon$ with respect to the \emph{field variables}.

For now, we discuss the steps necessary to analyze the performance of DPG with respect to a non-canonical test norm. We require a priori that the test norm has separable $\tau$ and $v$ components --- in other words, that there are no terms in the test norm that couple $\tau$ and $v$ together. Problem \eqnref{optvVar} then decouples, such that the components of the vector-valued test function $\left(v,\tau\right)$ can be solved for independently of each other. The decoupled variational problems are no longer systems but scalar equations in $\tau$ and $v$, for which it is easier to conclude whether or not there are boundary layers in the solutions (the avoidance of boundary layers in the test norm will be discussed in more detail in Section~\ref{sec:num_exp}, which describes our numerical experiments). \textbf{This will ensure that the resulting DPG method does not suffer from approximation errors in the optimal test functions}.

We begin with the following test norm:
\[
\left\|\left(v,\tau\right)\right\|^2_V \coloneqq \|v\|_{L^2}^2 + \epsilon\|\grad v\|_{L^2}^2 + \|\beta \cdot \grad v\|_{L^2}^2  + \frac{1}{\epsilon}\|\tau\|_{L^2}^2 + \|\div \tau\|_{L^2}^2.
\]
The use of this norm is problematic for practical computations; we will discuss the reasons why and present a modification of it in Section~\secref{sec:meshDep}.

We can see how this norm will differ from the canonical $H^1(\Omega_h)\times H({\rm div},\Omega_h)$ norm: the clearest difference is the fact that the gradient in the streamline direction is $O(1)$, while the full gradient is $O(\sqrt{\epsilon})$, so that, in our test norm, the streamline gradient of $v$ will be emphasized over the full gradient of $v$ for small $\epsilon$.

The choice of this test norm is implied by the mathematics of the adjoint problem. Roughly speaking, necessary conditions for the performance of DPG to not degenerate as $\epsilon \rightarrow 0$ are derived through analysis of specific test functions. For example, if $u$ is the first $L^2$ component of the solution to the variational problem defined in Section~\secref{sec:modelSec}, by choosing $(v,\tau) \in H^1(\Omega) \times H({\rm div},\Omega)$ such that 
\begin{align*}
\div \tau - \beta \cdot \grad v &= u \\
\frac{1}{\epsilon} \tau - \grad v &= 0,
\end{align*}
we have
\[
 \nor{u}_{L^2}^2 = b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right) \leq \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_{U,V} \nor{\left(v,\tau\right)}_V,
\]
and we recover the $L^2$ norm of $u$ from the bilinear form.

Let $\|a\| \lesssim \|b\|$ denote an $\epsilon$-independent bound; specifically, that $\|a\| \leq C\|b\|$ for a constant $C$ independent of $\epsilon$. Consequently, if for any $u\in L^2(\Oh)$, $\nor{\left(v,\tau\right)}_V\lesssim \nor{u}_{L^2}$, then dividing through by $\nor{u}_{L^2}$ gives the bound
\[
 \nor{u}_{L^2} \lesssim \nor{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)}_E.
\]
In other words, there is the guarantee that the $L^2$ error in $u$ is at least robustly bounded from above by the energy error. Then, if the energy error (which DPG minimizes) approaches zero, the $L^2$ error in $u$ will as well. The same exercise can be repeated for the stress $\sigma$, as well as the flux variables $\widehat{u}$, $\widehat{f}_n$.

This methodology gives constraints on the quantities found in the test norm; any quantity present in $\nor{\left(v,\tau\right)}_V$ must be shown to be bounded from above independently of $\epsilon$ by the load of the adjoint problem. However, showing this simply amounts to showing \textit{standard energy estimates} for $H^1$ and $H({\rm div})$-conforming finite elements. A more detailed discussion on the reasoning behind the construction of test norms can be found in \cite{DPGrobustness}.

The second step will be to \textbf{show the equivalence of the energy norm to explicit norms on $U$}. Since we do not generally have a closed form expression for the DPG energy norm, we seek to understand the behavior of DPG by finding a norm on $U$ to which the DPG energy norm is equivalent. Since $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U$ is a group variable from a tensor product space, we construct norms on $U$ through the combination of norms on $u$, $\sigma$, $\widehat{u}$, and $\widehat{f}_n$. Specifically, we use the norm on $U$ 
\begin{equation}
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \left\|\widehat{u}\right\|^2 + \left\|\widehat{f}_n\right\|^2.
\end{equation}
For equivalence between norms, two constants are specified. However, since this norm on $U$ is a norm on four separate variables, we can specify not just two but eight equivalence constants.\footnote{Sharper estimates are attainable if these constants are allowed to vary over the mesh $\Oh$. See Section~\ref{sec:main_bounds} for a discussion.} In order to simplify analysis, we phrase this equivalence statement in an alternative form.

Let $\nor{\cdot}_E \coloneqq \nor{\cdot}_{U,V}$, the energy norm induced by the test norm described above. We seek the bound of $\nor{\cdot}_E$ from above and below:
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2},
\]
where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are defined as scaled combinations of the norms on $u, \sigma, \widehat{u}$, and $\widehat{f}_n$
\begin{equation}
\eqnlab{uNorms}
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i}^2 \coloneqq \left(C_u^i\|u\|\right)^2 + \left(C_\sigma^i\|\sigma\|\right)^2 + \left(C_{\widehat{u}}^i\|\widehat{u}\|\right)^2 + \left(C_{\widehat{f}_n}^i\|\widehat{f}_n\|\right)^2,\quad i = 1,2
\end{equation}
Our goal is to explicitly derive the equivalence constants 
%$C^1_u,\ldots, C^1_{\widehat{f}_n}$ and $C^2_u,\ldots, C^2_{\widehat{f}_n}$ 
that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependency on $\epsilon$. To do so, we need a relation between trial norms on $U$ and test norms on $V$.

Recall from Section~\secref{energyPair} that every test norm induces a corresponding trial norm, and vice versa. Let $\|\cdot\|_{U,1} \simeq \|\cdot\|_{U,2}$ mean that the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are equivalent, with equivalence constants independent of $\epsilon$. By equivalence of finite dimensional norms and the discussion in Section~\secref{energyPair} on the duality between test norms/energy norms, the norms \eqnref{uNorms} on $U$ induce the equivalent test norms on $\left(v,\tau\right) \in H^1(\Oh)\times H({\rm div},\Oh)$
\begin{align*}
\left\|\left(v,\tau\right)\right\|_{V,{U,i}} &\simeq \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \jump{\tau_n}, \widehat{u} \rangle_{\Gamma_-\cup \Gh^0} + \langle \widehat{f}_n, \jump{v} \rangle_{\Gamma_+ \cup \Gh^0}}{C_u^i\|u\| + C_\sigma^i\|\sigma\| + C_{\widehat{u}}^i\|\widehat{u}\|+ C_{\widehat{f}_n}^i\|\widehat{f}_n\|}\\
& \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle \jump{\tau\cdot n}, \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_{\widehat{f}_n}^i}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, \jump{v}\rangle}{\|\widehat{f}_n\|},
\end{align*}
where $f$ and $g$ are defined element-wise over $\Oh$ as 
\begin{align*}
g &\coloneqq \div \tau - \beta \cdot \grad v\\
f &\coloneqq \epsilon^{-1}\tau + \grad v.
\end{align*}
By definition of the norms on the quantities defined on the skeleton $\Gh$, this gives the characterization of the induced test norm 
\[
\|\left(v,\tau\right)\|_{V,{U,i}} \simeq \frac{1}{C_u^i}\|g\| + \frac{1}{C_\sigma^i}\|f\| + \frac{1}{C_{\widehat{u}}^i}\|\jump{\tau\cdot n}\| + \frac{1}{C_{\widehat{f}_n}^i}\|\jump{v}\|, \quad i = 1,2.
\]
We can now use this relation to compare different norms on $U$ by comparing their induced norms on $V$ (recall that showing a robust inequality between two norms on $U$ is equivalent to showing the robust \textit{reverse} inequality in the induced norms on $V$). Namely, we can show the bound of $\nor{\cdot}_{U,1} \lesssim \nor{\cdot}_E$ by showing the bound $\nor{\left(v,\tau\right)}_{V,U,1} \gtrsim \nor{\left(v,\tau\right)}_{V}$, and likewise for $\nor{\cdot}_E \lesssim \nor{\cdot}_{U,2}$.

Since the techniques used to show such bounds are more involved, we break the procedure up into two steps:
\begin{enumerate}
\item{}Decompose test functions $(v,\tau)$ into three separate, more easily analyzable components (Section~\ref{sec:strategy2}).
\item{}Derive adjoint estimates (Section~\ref{sec:strategy3}).
\end{enumerate}

\subsubsection{Decomposition into analyzable components}
\label{sec:strategy2}

Having reduced the problem of comparing norms on $U$ to the comparison of norms on $V$, we break the analysis of $\left(v,\tau\right) \in V$ into the analysis of three subproblems.  Define the decomposition
\[
\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
\]
where $\left(v_1,\tau_1\right)$ satisfies 
\begin{align*}
\epsilon^{-1}\tau_1 + \grad v_1 &= 0 ,\\
\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g, 
\end{align*} 
and $\left(v_2,\tau_2\right)$ satisfies
\begin{align*}
\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f, \\
\div \tau_2 - \beta\cdot \grad v_2 &= 0.
\end{align*}
Both $(v_1,\tau_1), (v_2,\tau_2) \in H({\rm div}; \Omega)\times H^1(\Omega)$ are understood to satisfy these relations in a conforming sense over the domain $\Omega$; however, the divergence of $\tau$ and gradient of $v$ on the right hand side are still understood to be taken in an element-wise fashion.

We will additionally require both $\left(v_1,\tau_1\right), \left(v_2,\tau_2\right)$ to satisfy the adjoint homogeneous boundary conditions
\begin{align}
\tau_i\cdot n &= 0, \quad \text{on }\Gamma_- \label{bc_1}\\
v_i &= 0, \quad \text{on } \Gamma_+ \label{bc_2}
\end{align}
for $i = 1, 2$. The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific boundary conditions above removes the contribution of the jump terms over the skeleton $\Gh$ in the bilinear form, allowing us to analyze field terms in the induced test norms separately from  the boundary/jump terms.

Finally, by construction, $\left(v_0,\tau_0\right) \in H^1(\Oh) \times H({\rm div},\Oh)$ must satisfy 
\begin{align*}
\epsilon^{-1}\tau_0 + \grad v_0 &= 0\\
\div \tau_0 - \beta\cdot \grad v_0 &= 0
\end{align*}
with jumps
\begin{align*}
\jump{v_0} &= \jump{v}, \quad \text{on }\Gh^0\\
\jump{\tau_0 \cdot n} &= \jump{\tau \cdot n}, \quad \text{on }\Gh^0.
\end{align*}
and boundary conditions
\begin{align*}
v_0 &= v, \quad \text{on } \Gamma_+ \\
\tau_0 \cdot n &= \tau \cdot n, \quad \text{on } \Gamma_-\cup \Gamma_0. 
\end{align*}
Notice that the evaluation the bilinear form $b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(v,\tau\right)\right)$ with each specific test functions returns only one part of the bilinear form. Furthermore, by choosing the proper loads $g = u$ and $f=\sigma$, we can recover from the bilinear form the norms of $u$ and $\sigma$ (as described in Section~\secref{sec:testNormSec}), as well as the norms on $\widehat{u}$, and $\widehat{f}_n$.\footnote{To recover the norms on $\widehat{u}$, and $\widehat{f}_n$, the loads $f$, and $g$ must be zero, and the jumps of the test function $(v,\tau)$ must be chosen specifically.}

We have now decomposed an arbitrary test function $\left(\tau,v\right)$ into a discontinuous contribution and two continuous contributions.  Recall that our goal is to show the robust bound from above and below of the DPG energy norm by $\|\cdot \|_{U,1}$ and $\|\cdot \|_{U,2}$:
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
\]

>>>>

The majority of this chapter will focus on the convection-diffusion problem using the abstract theory that we have discussed in the previous chapter. In particular, we shall use the DPG method based on the ultra-weak formulation with optimal test functions to solve this model problem and analyze its behavior as $\epsilon\rightarrow 0$. Our goal is to show the robustness of the method with respect to $\epsilon$ (for a given test norm), and demonstrate its usefulness as a numerical method for solving singular-perturbed problems.  In particular, we will examine three different choices of test norms on $V$ -- an ideal norm (which returns good results, but whose test functions are difficult to approximate), a robust norm (which is easy to approximate and computationally efficient to assemble but still returns good results over a range of $\epsilon$), and finally, a coupled, robust test norm that borrows ideas from both the ideal and robust norm.\footnote{This third test norm is motivated by observed numerical difficulties; the precise shortcomings of the previous robust test norm are not completely understood, though a possible explanation is offered for both the issues encountered by the robust norm and the success of the coupled robust test norm in overcoming these issues.}

@@

We consider the following model convection-diffusion problem on a domain
$\Omega \subset \mathbb{R}^d$ with boundary $\pO \equiv \Gamma$
\begin{equation}
\div (\beta u) - \epsilon\Delta u = f  \in \L \label{primal},
\end{equation}
which can be cast into the first order form on the group variable
$\LRp{u,\sigma}$ as
\begin{equation}
\eqnlab{CDstrong}
A \LRp{u,\sigma} \coloneqq \LRs {
\begin{array}{c}
\div (\beta u - \sigma) \\ \frac{1}{\epsilon}\sigma - \grad u
\end{array}} = \LRs{
\begin{array}{c}
f \\ 0
\end{array}
}.
\end{equation}
Using the abstract ultra-weak formulation developed in Section
\secref{abstractUweak} for the first order system of PDEs \eqnref{CDstrong} we
obtain
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),
\left( v, \tau \right)\right) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} - \LRa{
\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{ \widehat{f}_n,
  \jump{v} }_{\Gh},
\end{align*}
where $\LRp{v, \tau}$ is the group test function. It should be pointed
out that the divergence and gradient operators are understood to act
element-wise on test functions $\LRp{v, \tau}$ in the broken graph
space $ D\LRp{A_h^*} \coloneqq  H^1(\Oh) \times H({\rm div}, \Oh)$, but
globally as usual on conforming test functions, i.e.\ $ \LRp{v, \tau}
\in  H^1(\Omega) \times H({\rm div}, \Omega)$. It follows that the
canonical norm on this test space can be written as
\[
\|\left(v, \tau\right)\|_V^2 = \|\left(v, \tau\right)\|_{H^1(\Oh) \times H({\rm div},\Oh)}^2
= \sum_{K\in \Oh} \|\left(v, \tau\right)\|_{H^1(K) \times H({\rm
    div},K)}^2,
\]
where
\[
\|\left(v, \tau \right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2.
\]

In order to define the proper norm on the trial space, boundary
conditions need to be specified. We begin by splitting the boundary
$\Gamma$ as follows
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm
  (inflow)},\\ 
  \Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\}
\quad {\rm (outflow)},\\ 
\Gamma_{0} &\coloneqq \{x\in \Gamma;
\beta_n(x) = 0\},
\end{align*}
where $\beta_n \coloneqq \beta \cdot n$.
On the inflow boundary, we apply the inflow boundary condition $$u = u_{\rm in} \quad \text{on }\Gm.$$  On the outflow boundary, we apply standard homogeneous Dirichlet boundary conditions
\[
u = 0, \quad \text{on } \Gp.
\]
